### 2016-10-05 robust-software.tex
Don't recommend writing docs because...

\item
``Write documentation'' is not one of our ten rules.
Explain in the conclusion that we think this is really important,
but it's not the software per se.
We also don't think people are unlikely do it during normal development,
and we don't want to recommend practices that people won't actually adopt.

@@

>>>>

@@

Another notable omission is documentation.
We think it is very important for developers to do this,
but our experience is that people are unlikely do it during normal development,
and we don't want to recommend practices that people won't actually adopt.
